\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-26 paper.tex
evaluation-update

\author{Paper \# 56, 18 pages}
% \author{Firstname Lastname}
% \authornote{Note}
% \orcid{1234-5678-9012}
% \affiliation{%
%   \institution{Affiliation}
%   \streetaddress{Address}
%   \city{City} 
%   \state{State} 
%   \postcode{Zipcode}
% }
% \email{email@domain.com}

@@

\begin{figure}
\begin{center}
\includegraphics [width=0.9\columnwidth] {fig/inter-DC-WAN-V3.pdf}
\caption{System architecture of $\mathsf{BATE}$}
\label{pic-overview}
\end{center}
\end{figure}

@@

 \begin{figure}
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology with failure probabilities}
\label{testbed}
\end{center}
\end{figure}
%
%
% \begin{figure}
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/testbed-admit.pdf}
%\caption{Admission control comparison.}
%\label{admission-control2}
%\end{center}
%\end{figure}
%
%
%
%\begin{figure}
%\centering
%\subfigure[Availability satisfaction]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
%\subfigure[Admission time]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-public-2.pdf}}
%\caption{Traffic scheduling comparison.}
%\label{testbed-traffic-scheduling}
%\end{figure}

\begin{figure*}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-admit.pdf}}
\subfigure[Bandwidth availability]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
\subfigure[Profit loss after failures]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbet-loss2.pdf}}
\subfigure[Overall profit gain]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/overall-profit.pdf}}
\caption{BA demands arrive with poisson process and their duration are with exponential distribution.}
\label{e2}
\end{figure*}

@@

\section{Evaluation} \label{evaluation}
In this section, we use a small testbed and larger scale trace driven simulations  to evaluate the performance of $\mathsf{BATE}$. 
On the testbed, we also implement another two state-of-the-art TE algorithms considering network availability, i.e., FFC \cite{FFC} and TEAVAR \cite{Teavar}. 
For simulation, we implement more TE algorithms, including xxx. 
All codes for our implementation and evaluation will be published, 
so that interested readers can use them in their own environments or make further improvements.

Our main results are as follows:

%We begin by describing the experimental framework ($\S$ \ref{setting}). 
%We show the performance of $\mathsf{BATE}$ through answering the following specific questions:
%compared with the latest TE schemes like FFC and TEAVAR, BATE can meet the availability SLAs of 40% more bandwidth demands, and when network failure causes SLA violations, it can retain 30% more profit under a simple pricing and refunding model.
(1) $\mathsf{BATE}$ consistently ourperforms latests TE algorithms under various topologies, traffic matrices and failure scenarios. With $\mathsf{BATE}$, up to 40\% more bandwidth availability demands can be successfully fulfilled, and 30\% more profit can be retained when failures occur.

@@

@@

\begin{figure}
\centering
\subfigure[No extra admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/fixed-scheduling.pdf}}
\subfigure[Fixed admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/no-fixed.pdf}}
\caption{Traffic scheduling schemes comparisons.}
\label{scheduling-benefit}
\end{figure}

@@

%
%
%
%
%
%
%
 \begin{figure}[h]
\begin{center}
\includegraphics [width=0.7\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}

@@

>>>>

\author{Paper \# 56, 17 pages}
% \author{Firstname Lastname}
% \authornote{Note}
% \orcid{1234-5678-9012}
% \affiliation{%
%   \institution{Affiliation}
%   \streetaddress{Address}
%   \city{City} 
%   \state{State} 
%   \postcode{Zipcode}
% }
% \email{email@domain.com}

@@

\begin{figure}
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/inter-DC-WAN-V3.pdf}
\caption{System architecture of $\mathsf{BATE}$}
\label{pic-overview}
\end{center}
\end{figure}

@@

 \begin{figure}
\begin{center}
\includegraphics [width=0.75\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology with failure probabilities}
\label{testbed}
\end{center}
\end{figure}
%
%
% \begin{figure}
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/testbed-admit.pdf}
%\caption{Admission control comparison.}
%\label{admission-control2}
%\end{center}
%\end{figure}
%
%
%
%\begin{figure}
%\centering
%\subfigure[Availability satisfaction]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
%\subfigure[Admission time]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-public-2.pdf}}
%\caption{Traffic scheduling comparison.}
%\label{testbed-traffic-scheduling}
%\end{figure}

\begin{figure*}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-admit.pdf}}
\subfigure[Bandwidth availability]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
\subfigure[Profit loss after failures]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbet-loss2.pdf}}
\subfigure[Overall profit gain]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/overall-profit.pdf}}
\caption{Demands arrive with poisson process and their duration are with exponential distribution.}
\label{e2}
\end{figure*}

@@

\section{Evaluation} \label{evaluation}
In this section, we use a small testbed and larger scale trace driven simulations  to evaluate the performance of $\mathsf{BATE}$. 
On the testbed, we also implement another two state-of-the-art TE algorithms considering network availability, i.e., FFC \cite{FFC} and TEAVAR \cite{Teavar}. 
For simulation, we implement more TE algorithms, including SWAN \cite{swan}, SMORE \cite{SMORE} and B4 \cite{B4}. 
All codes for our implementation and evaluation will be published, 
so that interested readers can use them in their own environments or make further improvements. 
Our main results are as follows:

%We begin by describing the experimental framework ($\S$ \ref{setting}). 
%We show the performance of $\mathsf{BATE}$ through answering the following specific questions:
%compared with the latest TE schemes like FFC and TEAVAR, BATE can meet the availability SLAs of 40% more bandwidth demands, and when network failure causes SLA violations, it can retain 30% more profit under a simple pricing and refunding model.
(1) $\mathsf{BATE}$ consistently outperforms latests TE algorithms under various topologies, traffic matrices and failure scenarios. With $\mathsf{BATE}$, up to 40\% more bandwidth availability demands can be successfully fulfilled, and 30\% more profit can be retained when failures occur.

@@

(3)  $\mathsf{BATE}$ has stable performance: it doesn't depend on specific network topology, routing schemes, etc.

@@

\begin{figure}
\centering
\subfigure[No extra admission control]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/fixed-shuduling.pdf}}
\subfigure[Fixed admission control]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/fixed-scheduling.pdf}}
\caption{Traffic scheduling schemes comparisons.}
\label{scheduling-benefit}
\end{figure}

@@

%
%
%
%
%
%
%

@@

 \begin{figure}[t]
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}
